Resolving Limits Faced by Classical Machine Learning Approaches: Areas of Application for Collaborative Interactive Learning Techniques

### 2018-09-12 CILApplicationAreas.tex
Finish publishable version

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Christoph Sonntag$^1$}
\IEEEauthorblockA{$^1$Intelligent Systems Group, University of Passau, Innstrasse 70, Passau, Germany\\
sonntagc@fim.uni-passau.de}
}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The area of \textit{Machine Learning} has experienced a high 
level of research interest in the last few years with it's underlying 
theory reaching back far into the 18th century. Due to minimal 
costs for computation and the massive availability of data in the 
Internet recent research interest has been mainly focused on 
\textit{Automatic Machine Learning}. In this paradigm a model 
(e.g.\ classifier, \dots) is being trained with a pre-labeled training 
set in order to make predictions on unknown unlabeled data. Problems arise 
in domains where data is rarely available or where the labeling process is 
too expensive (computationally or economically). Furthermore, real-world data 
can be uncertain, incomplete or contain noisy data. In these cases 
full automation is not reliable enough or even infeasible for specific 
domains. However, robust and trustworthy results are mandatory in a lot of 
applications like health informatics or autonomous vehicles. 
Therefore, systems are needed that interactively integrate knowledge from 
various experts, which can be collaborating humans or machines, in order 
to continuously improve results over a system's whole lifetime: So called 
\textit{Collaborative Interactive Learning (CIL)} systems.
This paper contributes in presenting an overview of classical \textit{Machine Learning} 
approaches in comparison with CIL and outlines possible areas of application. 
\end{abstract}

\section{Introduction}\label{sec:intro}
As with most concepts, there is no canonical 
definition for the term \textit{Machine Learning (ML)} but at its most basic form it 
can be described as algorithms that learn from a given set of training examples 
$\{(x_i, y_i)\}$ of inputs $x_i$ and outputs $y_i$ in order to 
make predictions on unknown input data. According to Tom 
Mitchell, a computer scientist from Carnegie Mellon University,  ML tries 
to answer how we can build algorithms that automatically improve through 
experience and which fundamental laws govern all these learning processes\cite{ML:mitchell}.
The area of ML in general is a fast-growing discipline at the intersection of statistics 
and computer science and has experienced massive research interest in the last decades.
With its various application possibilities it has also been an interesting branch for 
economists and entrepreneurs.
Since ML scenarios like \textit{supervised}, \textit{unsupervised} and 
\textit{semi-supervised} learning, which we will cover later, are heavily data-driven, 
the internet with its massive amount of data has contributed to the further development 
of research in the area of fully automated learning algorithms. Today, we can see the 
results in a variety of applications\cite{FoundationsOfML:mohri}\cite{DisciplineOfML:mitchell} 
described in more detail in Section~\ref{sec:algos}.

@@

\section{Collaborative Interactive Learning}\label{sec:cil}
The term \textit{Collaborative Interactive Learning (CIL)} is a relatively new concept of systems which 
includes other domain experts (humans) and CIL systems in the decision/prediction making process 
as shown in Figure~\ref{fig:CIL}. It describes the vision of a new 
generation of systems with
\begin{itemize}
    \item lifelong learning capabilities in order to continuously improve its 
        knowledge base (\textit{learning})
    \item and the ability to exchange knowledge with other CIL systems as well as humans 
        in order to improve the own knowledge and learning process and the one of other entities in a 
        bi-directional way (\textit{interactive}, \textit{collaborative})\cite{CIL:sick}.
\end{itemize}
\begin{figure}[!h]
\centering
\includegraphics[width=3.5in]{images/CIL}
\caption{Interaction between heterogeneous systems in CIL.}
\label{fig:CIL}
\end{figure}
So the main difference to classical ML is the possibilty to adapt and optimise itself during run-time 
towards new situations without having been specifically trained for these use-cases, whereas classical ML 
systems have had to be fed with a sufficient amount of relevant training data\cite{CIL:sick}\cite{Organic:schloer}.
Furthermore, CIL systems interact with their environment in order to not rely on a single training data set. 
They collect data from several other sources (including humans) to validate already existing information and to 
gather additional data from other sources. In this way, CIL systems can be used in a lot of application areas where 
environments are constantly changing or training data is rarely available.
In general, we can still distinguish between \textit{dedicated} (concentrating mostly on one defined learning process, 
other interacting agents are largely human experts) and \textit{opportunistic} CIL (changing environments, heterogeneous 
sources of information)\cite{CIL:sick}, 
but we want to concentrate on general areas of application in this paper.

@@

Over the last decades, ML has developed significantly and has become an area of
research interest for many different actors, which makes it difficult to divide learning 
strategies into several categories. Different researchers are using different approaches 
\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
However, in the following section I want to present five common strategies\cite{FoundationsOfML:mohri}.

\subsection{Supervised learning}
Basically supervised learning is the way of learning from labeled examples and making predictions 
for all unseen points. This is the most basic concept of ML and is used in a variety of applications 
where labeled data is easy to obtain. Spam mail detection for instance is a case where supervised learning 
techniques are - among others - used.
Many current mail programs have built-in spam detection which originally used
simple regular expressions in order to detect phrases commonly used in spam mails.
With state-of-the-art ML techniques it is not only possible for a mail program to 
query for a number of words but to recognise patterns of how spam mails are constructed and 
to adapt itself to new types of spam.
Supervised Learning methods have also been successfully applied in domains where it's 
important to extract information from images such as detecting and classifying 
objects or recognizing handwritten characters. Image 
recognition and OCR are therefore for example used in medical diagnosis to 
detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
stay on track or in post-offices to sort envelopes with hand-written addresses
\cite{DisciplineOfML:mitchell}.

\subsection{Unsupervised learning}
In contrast to supervised learning, the learner receives only 
unlabeled training data and makes predictions for all unseen points in this concept. This technique is 
relatively similar to the way infants learn new things (e.g.\ learning a language) and 
is used, for example, in clustering data into groups, which we will discuss later\cite{BrainInf:holzinger}.
Furthermore, nearly all current search machines use unsupervised learning strategies in one fashion or another. 
They mainly use these techniques for \textit{(1) Ranking}, \textit{(2) User classification}\cite{DisciplineOfML:mitchell} 
in order to offer personalized search results and for \textit{(3) Query classification} in order to ``understand'' a 
users query and to provide further meaningful information.

@@

\subsection{Reinforcement Learning}\label{reinforcement}
Reinforcement learning is probably the oldest approach and a potentially important one for CIL because 
it constantly tries to reinforce its learning process and improve its behavior. 
The learner constantly interacts with its environment to gain new information. A second instance interpretes the 
actions a learner carries out and rewards it depending on the actions outcome for the environment. The goal of 
the learner now is to maximize its reward over several repetitions. 
However, he is in conflict with using the information which has already been discovered by his actions 
or with getting more information through further actions. Reinforcement Learning has been successfully 
applied to various problems. 
Computer games usually offer a multiplayer mode where a user can interact and 
play the game even without a human opponent. For games with a small number of 
possible moves after each turn, and therefore a relatively small game tree containing 
all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
It figures out which next move would minimize the worst-case scenario for all subsequent 
moves. Therefore, it needs to know all possible moves, which can easily become computationally 
infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
250 (AlphaGo) possible subsequent game states. 
Therefore, game artificial intelligences like AlphaGo are using Reinforcement Learning in order to gain 
experience by themselves\cite{Alpha:silver}.

@@

\subsection{Self-Optimization}
In order to deliver reasonable output, a systems needs to constantly improve itself over its lifetime. Thus, parts of 
the system have to analyze decisions made during run-time.
CIL systems optimize themselves by applying various strategies of ML to expand their knowledge.

@@

\subsection{Clustering}
Clustering is the perfect example of a starting point without sufficient information about an amount of data. 
The basic goal here is to divide a data set into homogeneous groups of individual data points in order to create structure in it.
In this context data points must be checked for similarity in some way.
Clustering is used, for example, in most recommendation systems of popular internet applications 
(\textit{Netflix} movie recommendations, \textit{YouTube} Video Tags\cite{YouTube:pasca}) to group similar tags or find groups 
of people with a similar taste in movies.
Furthermore, clustering can be used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified\cite{DJ:frankowski}.

@@

What all cluster algorithms have in common is that they need a way to compare data points for similarity respectively distance 
in order to find centers.
Classically, data points are tried to be displayed in an n-dimensional metric space and, for example, their Euclidean distance is measured for similarity.
The Euclidean distance between two data points $p = (p_1, p_2, \dots, p_n)$ and $q = (q_1, q_2, \dots, q_n)$ and thus their
similarity, when a small result means more similar, is defined as
\begin{equation*}
    similarity(p, q) = \sqrt{\sum_{i=1}^{n} (q_i - p_i)^{2}}.
\end{equation*}

@@

Another area of application in the field of medical research also takes advantage of human puzzle-solving intuition. 
For years the project "foldit" of the University of Washington has achieved remarkable results\cite{Foldit:results} from the gamification of a problem related to biology.
The researchers have developed a game that helps them to optimize and predict possible protein structures with the help of 
players\cite{Foldit:web}.
Proteins can fold in a number of different ways. Even with smaller proteins, the number of possible folds can be extremely high due to their many degrees of freedom.
The aim of the game is to determine the optimal folding and thus the "most comfortable" state of a protein in order to be able to develop appropriate drugs for and with this shape.
Since the structure determines the function of a protein\cite{Foldit:web}, new forms can also be used to treat diseases such as AIDS or cancer more effectively.

So we already see a system in this field that at least involves the human being as a collective form of knowledge acquisition in the solution of complex problems, even if not directly with technical systems.
The next step towards CIL in this area could be to incorporate the results of human puzzle-solving into the calculations and decisions of ML systems in order to proactively support humans (bi-directional way of inputs, see Section~\ref{sec:intro}) in finding solutions 
for example by excluding unpromisingfls.

\subsection{Industry and Manufacturing}
The primary goal in manufacturing is to keep production up and running under almost all circumstances. 
Even short downtimes of production lines result in high sales losses for companies.
This is why it is important to keep an eye on the wear of work equipment, production lines and the condition of machines in general at all times.
Current systems already use various ML techniques\cite{Manu:wuest} to cover these applications.

For CIL-systems, it is conceivable, in addition to the sensor data used by the devices to "measure" wear, to call in expert knowledge, so that rare cases that are easily recognisable as a suspicious situation for humans, can be identified at an early stage by the whole system.
In this process, a CIL system must estimate at runtime which expert should be asked what and when in order 
to achieve maximum information content.

@@

Not only technical difficulties have to be overcome, but also social ones. In order to use ML techniques effectively, 
at least a minimum amount of data has to be provided in order to be analyzed. To do this, we need to decide 
to what extent we are willing to disclose our data for the benefits of CIL systems and ML in general.
Inhibitions in human-machine communication and interaction must also be overcome for CIL systems to be used 
successfully and productively.

\begin{thebibliography}{1}
\bibitem{ML:mitchell}
    Mitchell, T. M. (1997). Machine learning. 1997. Burr Ridge, IL: McGraw Hill, 45(37), 870-877.
\bibitem{FoundationsOfML:mohri}
    Mohri, M., Rostamizadeh, A., \& Talwalkar, A. (2012). Foundations of machine learning. MIT press.
\bibitem{DisciplineOfML:mitchell}
    Mitchell, T. M. (2006). The discipline of machine learning (Vol. 9). Carnegie Mellon University, School of Computer Science, Machine Learning Department.
\bibitem{Prog2:bachmaier}
    Bachmaier, C. (2017). Lecture. Programming II\@. Faculty for Informatics and Mathematics, University of Passau, Germany.
\bibitem{CIL:sick}
    Sick, B., Oeste-Rei{\ss}, S., Schmidt, A., Tomforde, S., \& Zweig, A. K. (2018). Collaborative Interactive Learning. Informatik-Spektrum, 41(1), 52-55.
\bibitem{Structure:corne}
    Corne, D., Dhaenens, C., \& Jourdan, L. (2012). Synergies between operations research and data mining: The emerging use of multi-objective approaches. European Journal of Operational Research, 221(3), 469-479.
\bibitem{ActiveToDedicated:calma}
    Calma, A., Leimeister, J. M., Lukowicz, P., Oeste-Rei{\ss}, S., Reitmaier, T., Schmidt, A., \dots \& Zweig, K. A. (2016, April). From active learning to dedicated collaborative interactive learning. In ARCS 2016; 29th International Conference on Architecture of Computing Systems; Proceedings of (pp. 1-8). VDE.
\bibitem{BrainInf:holzinger}
    Holzinger, A. (2016). Interactive machine learning for health informatics: when do we need the human-in-the-loop?. Brain Informatics, 3(2), 119-131.
\bibitem{Alpha:silver}
    Silver, D., Hassabis, D. (2016, January). AlphaGo: Mastering the ancient game of Go with Machine Learning. Google AI Blog. Retrieved from \url{https://ai.googleblog.com/2016/01/alphago-mastering-ancient-game-of-go.html} on August 24, 2018. 
\bibitem{MLStudiesUsingCheckers:samuel}
    Samuel, A. L. (1959). Some studies in machine learning using the game of checkers. IBM Journal of research and development, 3(3), 210-229.
\bibitem{Organic:schloer}
    M{\"u}ller-Schloer, C., von der Malsburg, C., \& W{\"u}rt, R. P. (2004). Organic computing. Informatik-Spektrum, 27(4), 332-336.
\bibitem{Organic:schmeck}
    Schmeck, H. (2005, May). Organic computing-a new vision for distributed embedded systems. In Object-Oriented Real-Time Distributed Computing, 2005. ISORC 2005. Eighth IEEE International Symposium on (pp. 201-203). IEEE.
\bibitem{DJ:frankowski}
    Zhou, C., Frankowski, D., Ludford, P., Shekhar, S., \& Terveen, L. (2004, November). Discovering personal gazetteers: an interactive clustering approach. In Proceedings of the 12th annual ACM international workshop on Geographic information systems (pp. 266-273). ACM.
\bibitem{YouTube:pasca}
    Toderici, G., Aradhye, H., Pasca, M., Sbaiz, L., \& Yagnik, J. (2010, June). Finding meaning on youtube: Tag recommendation and category discovery. In Computer Vision and Pattern Recognition (CVPR), 2010 IEEE Conference on (pp. 3447-3454). IEEE.
\bibitem{Foldit:web}
    The Science Behind Foldit. (n.d.). University of Washington, Departments of Computer Science \& Engineering and Biochemistry. Retrieved from \url{https://fold.it/portal/info/about} on June 29, 2018. 
\bibitem{Foldit:results}
    Boyle, A. (2011, September). Gamers solve molecular puzzle that baffled scientists. Cosmic Log.\\
    Retrieved from \url{https://cosmiclog.nbcnews.com/_news/2011/09/18/7802623-gamers-solve-molecular-puzzle-that-baffled-scientists} on June 29, 2018.
\bibitem{Manu:wuest}
    Wuest, T., Weimer, D., Irgens, C., \& Thoben, K. D. (2016). Machine learning in manufacturing: advantages, challenges, and applications. Production \& Manufacturing Research, 4(1), 23-45.
\end{thebibliography}

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Christoph Sonntag$^1$}
\IEEEauthorblockA{$^1$Intelligent Systems Group, University of Passau, Innstrasse 43, Passau, Germany\\
sonntagc@fim.uni-passau.de}
}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The area of \textit{Machine Learning} has experienced a high 
level of research interest in the last few years with it's underlying 
theory reaching back far into the 18th century. Due to minimal 
costs for computation and the massive availability of data in the 
Internet recent research interest has been mainly focused on 
\textit{Automatic Machine Learning}. In this paradigm a model 
(e.g.\ classifier, \dots) is being trained with a pre-labeled training 
set in order to make predictions on unknown unlabeled data. Problems arise 
in domains where data is rarely available or where the labeling process is 
too expensive (computationally or economically). Furthermore, real-world data 
can be uncertain, incomplete or contain noisy data. In these cases 
full automation is not reliable enough or even infeasible for specific 
domains. However, robust and trustworthy results are mandatory in a lot of 
applications like health informatics or autonomous vehicles. 
Therefore, systems are required which interactively integrate knowledge from 
various experts, which can be collaborating humans or machines, in order 
to continuously improve results over a system's whole lifetime: So called 
\textit{Collaborative Interactive Learning (CIL)} systems.
This paper contributes in presenting an overview of classical \textit{Machine Learning} 
approaches in comparison with CIL and outlines possible areas of application. 
\end{abstract}

\section{Introduction}\label{sec:intro}
As with most concepts, there is no canonical 
definition for the term \textit{Machine Learning (ML)} but at its most basic form it 
can be described as algorithms that learn from a given set of training examples 
$\{(x_i, y_i)\}$ of inputs $x_i$ and outputs $y_i$ in order to 
make predictions on unknown input data. According to Tom 
Mitchell, a computer scientist from Carnegie Mellon University,  ML tries 
to answer how we can build algorithms that automatically improve through 
experience and which fundamental laws govern all these learning processes\cite{ML:mitchell}.
The area of ML in general is a fast-growing discipline at the intersection of statistics 
and computer science and has experienced massive research interest in the last decades.
With its various application possibilities it has also been an interesting branch for 
economists and entrepreneurs.
Since ML scenarios like \textit{supervised}, \textit{unsupervised} and 
\textit{semi-supervised} learning, which will be covered later, are heavily data-driven, 
the internet with its massive amount of data has contributed to the further development 
of research in the area of fully automated learning algorithms. Today, the results can 
be seen in a variety of applications\cite{FoundationsOfML:mohri}\cite{DisciplineOfML:mitchell} 
described in more detail in Section~\ref{sec:algos}.

@@

\section{Collaborative Interactive Learning}\label{sec:cil}
The term \textit{Collaborative Interactive Learning (CIL)} is a relatively new concept of systems which 
include other domain experts (humans) and CIL systems in the decision/prediction making process 
as shown in Figure~\ref{fig:CIL}. It describes the vision of a new 
generation of systems with
\begin{itemize}
    \item lifelong learning capabilities in order to continuously improve its 
        knowledge base (\textit{learning})
    \item and the ability to exchange knowledge with other CIL systems as well as humans 
        in order to improve the own knowledge and learning process and the one of other entities in a 
        bi-directional way (\textit{interactive}, \textit{collaborative})\cite{CIL:sick}.
\end{itemize}
\begin{figure}[!h]
\centering
\includegraphics[width=3.5in]{CIL}
\caption{Interaction between heterogeneous systems in CIL.}
\label{fig:CIL}
\end{figure}
So the main difference to classical ML is the possibility to adapt and optimise itself during run-time 
towards new situations without having been specifically trained for these use-cases, whereas classical ML 
systems have had to be fed with a sufficient amount of relevant training data\cite{CIL:sick}\cite{Organic:schloer}.
Furthermore, CIL systems interact with their environment in order to not rely on a single training data set. 
They collect data from several other sources (including humans) to validate already existing information and to 
gather additional data from other sources. In this way, CIL systems can be used in a lot of application areas where 
environments are constantly changing or training data is rarely available.
In general, we can still distinguish between \textit{dedicated} (concentrating mostly on one defined learning process, 
other interacting agents are largely human experts) and \textit{opportunistic} CIL (changing environments, heterogeneous 
sources of information)\cite{CIL:sick}, 
but in order to give a general overview on areas of application, both will be considered equal in this paper.

@@

Over the last decades, ML has developed significantly and has become an area of
research interest for many different actors, which makes it difficult to divide learning 
strategies into several categories. Different researchers are using different 
approaches\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
However, in the following section I want to present five common strategies\cite{FoundationsOfML:mohri}.

\subsection{Supervised learning}
Basically supervised learning is the way of learning from labeled examples and making predictions 
for all unseen points. This is the most basic concept of ML and is used in a variety of applications 
where labeled data is easy to obtain. Spam mail detection for instance is a case where -- among 
others -- supervised learning techniques are used.
Many current mail programs have built-in spam detection which originally used
simple regular expressions in order to detect phrases commonly used in spam mails.
With state-of-the-art ML techniques it is not only possible for a mail program to 
query for a number of words but to recognise patterns of how spam mails are constructed and 
to adapt itself to new types of spam.
Supervised Learning methods have also been successfully applied in domains where it's 
important to extract information from images such as detecting and classifying 
objects or recognizing handwritten characters. Image 
recognition and OCR are therefore for example used in medical diagnosis to 
detect cancer on radiograms, in autonomous vehicles to detect obstacles and to 
stay on track or in post-offices to sort envelopes with hand-written 
addresses\cite{DisciplineOfML:mitchell}.

\subsection{Unsupervised learning}
In contrast to supervised learning, the learner receives only 
unlabeled training data and makes predictions for all unseen points in this concept. This technique is 
relatively similar to the way infants learn new things (e.g.\ learning a language) and 
is used, for example, in clustering data into groups, which will be discussed later\cite{BrainInf:holzinger}.
Furthermore, nearly all current search machines use unsupervised learning strategies in one way or another. 
They mainly use these techniques for \textit{(1) Ranking}, \textit{(2) User classification}\cite{DisciplineOfML:mitchell} 
in order to offer personalized search results and for \textit{(3) Query classification} in order to ``understand'' a 
users query and to provide further meaningful information.

@@

\subsection{Reinforcement Learning}\label{reinforcement}
Reinforcement learning is probably the oldest approach and a potentially important one for CIL because 
it constantly tries to reinforce its learning process and improve its behavior. 
The learner constantly interacts with its environment to gain new information. Another unit interprets the 
actions carried out by a learner and rewards it depending on the actions outcome for the environment. The goal of 
the learner now is to maximize its reward over several repetitions. 
However, he is in conflict with using the information which has already been discovered by his actions 
or with getting more information through further actions. Reinforcement Learning has been successfully 
applied to various problems. 
Computer games usually offer a multiplayer mode where a user can interact and 
play the game even without a human opponent. For games with a small number of 
possible moves after each turn, and therefore a relatively small game tree containing 
all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
It figures out which next move would minimize the worst-case scenario for all subsequent 
moves. Therefore, it needs to know all possible moves, which can easily become computationally 
infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
250 (AlphaGo) possible subsequent game states. 
Therefore, game artificial intelligences like AlphaGo are using Reinforcement Learning in order to gain 
experience by themselves\cite{Alpha:silver}.

@@

\subsection{Self-Optimisation}
In order to deliver reasonable output, a systems needs to constantly improve itself over its lifetime. Thus, parts of 
the system have to analyze decisions made during run-time.
CIL systems optimize themselves by applying various strategies of ML to expand their knowledge.

@@

\subsection{Clustering}
Clustering is the perfect example of a starting point without sufficient information about an amount of data. 
The basic goal here is to divide a data set into homogeneous groups of individual data points in order to create structure in it.
In this context data points must be checked for similarity in some way.
Clustering is used, for example, in most recommendation systems of popular internet applications 
(\textit{Netflix} movie recommendations, \textit{YouTube} Video Tags\cite{YouTube:pasca}) to group similar tags or find groups 
of people with a similar taste in movies.
Furthermore, clustering can be used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that ``important places'' of a person can be identified\cite{DJ:frankowski}.

@@

What all cluster algorithms have in common is that they need a way to compare data points for similarity respectively distance 
in order to find centers.
Classically, data points are tried to be displayed in a n-dimensional metric space and, for example, their Euclidean distance is measured for similarity.
The Euclidean distance between two data points $p = (p_1, p_2, \dots, p_n)$ and $q = (q_1, q_2, \dots, q_n)$ and thus their
similarity, when a small result means more similar, is defined as
\begin{equation*}
    similarity(p, q) = \sqrt{\sum_{i=1}^{n} (q_i - p_i)^{2}}.
\end{equation*}

@@

Another area of application in the field of medical research also takes advantage of human puzzle-solving intuition. 
For years the project ``foldit'' of the University of Washington has achieved remarkable results\cite{Foldit:results} from the gamification of a problem related to biology.
The researchers have developed a game that helps them to optimize and predict possible protein structures with the help of 
players\cite{Foldit:web}.
Proteins can fold in a number of different ways. Even with smaller proteins, the number of possible folds can be extremely high due to their many degrees of freedom.
The aim of the game is to determine the optimal folding and thus the ``most comfortable'' state of a protein in order to be able to develop appropriate drugs for and with this shape.
Since the structure determines the function of a protein\cite{Foldit:web}, new forms can also be used to treat diseases such as AIDS or cancer more effectively.

So we already see a system in this field that at least involves the human being as a collective form of knowledge acquisition in the solution of complex problems, even if not directly with technical systems.
The next step towards CIL in this area could be to incorporate the results of human puzzle-solving into the calculations and decisions of ML systems in order to proactively support humans (bi-directional way of inputs, see Section~\ref{sec:intro}) in finding solutions 
for example by excluding unpromising folds.

\subsection{Industry and Manufacturing}
The primary goal in manufacturing is to keep production up and running under almost all circumstances. 
Even short down times of production lines result in high sales losses for companies.
This is why it is important to keep an eye on the wear of work equipment, production lines and the condition of machines in general at all times.
Current systems already use various ML techniques\cite{Manu:wuest} to cover these applications.

For CIL systems, it is conceivable, in addition to the sensor data used by the devices to ``measure'' wear, to call in expert knowledge, so that rare cases that are easily recognisable as a suspicious situation for humans, can be identified at an early stage by the whole system.
In this process, a CIL system must estimate at run-time which expert should be asked what and when in order 
to achieve maximum information content.

@@

Not only technical difficulties have to be overcome, but also social ones. In order to use ML techniques effectively, 
at least a minimum amount of data has to be provided in order to be analyzed. To do so, we need to decide 
to what extent we are willing to disclose our data for the benefits of CIL systems and ML in general.
Inhibitions in human-machine communication and interaction must also be overcome for CIL systems to be used 
successfully and productively.

\begin{thebibliography}{1}
\bibitem{ML:mitchell}
    Mitchell, T. M. (1997). Machine learning. 1997. Burr Ridge, IL: McGraw Hill, 45(37), 870-877.
\bibitem{FoundationsOfML:mohri}
    Mohri, M., Rostamizadeh, A., \& Talwalkar, A. (2012). Foundations of machine learning. MIT press.
\bibitem{DisciplineOfML:mitchell}
    Mitchell, T. M. (2006). The discipline of machine learning (Vol. 9). Carnegie Mellon University, School of Computer Science, Machine Learning Department.
\bibitem{Prog2:bachmaier}
    Bachmaier, C. (2017). Lecture. Programming II\@. Faculty for Informatics and Mathematics, University of Passau, Germany.
\bibitem{CIL:sick}
    Sick, B., Oeste-Rei{\ss}, S., Schmidt, A., Tomforde, S., \& Zweig, A. K. (2018). Collaborative Interactive Learning. Informatik-Spektrum, 41(1), 52-55.
\bibitem{Structure:corne}
    Corne, D., Dhaenens, C., \& Jourdan, L. (2012). Synergies between operations research and data mining: The emerging use of multi-objective approaches. European Journal of Operational Research, 221(3), 469-479.
\bibitem{ActiveToDedicated:calma}
    Calma, A., Leimeister, J. M., Lukowicz, P., Oeste-Rei{\ss}, S., Reitmaier, T., Schmidt, A., \dots \& Zweig, K. A. (2016, April). From active learning to dedicated collaborative interactive learning. In ARCS 2016; 29th International Conference on Architecture of Computing Systems; Proceedings of (pp. 1-8). VDE.
\bibitem{BrainInf:holzinger}
    Holzinger, A. (2016). Interactive machine learning for health informatics: when do we need the human-in-the-loop?. Brain Informatics, 3(2), 119-131.
\bibitem{Alpha:silver}
    Silver, D., Hassabis, D. (2016, January). AlphaGo: Mastering the ancient game of Go with Machine Learning. Google AI Blog. Retrieved from \url{https://ai.googleblog.com/2016/01/alphago-mastering-ancient-game-of-go.html} on August 24, 2018. 
\bibitem{MLStudiesUsingCheckers:samuel}
    Samuel, A. L. (1959). Some studies in machine learning using the game of checkers. IBM Journal of research and development, 3(3), 210-229.
\bibitem{Organic:schloer}
    M{\"u}ller-Schloer, C., von der Malsburg, C., \& W{\"u}rt, R. P. (2004). Organic computing. Informatik-Spektrum, 27(4), 332-336.
\bibitem{Organic:schmeck}
    Schmeck, H. (2005, May). Organic computing-a new vision for distributed embedded systems. In Object-Oriented Real-Time Distributed Computing, 2005. ISORC 2005. Eighth IEEE International Symposium on (pp. 201-203). IEEE.
\bibitem{DJ:frankowski}
    Zhou, C., Frankowski, D., Ludford, P., Shekhar, S., \& Terveen, L. (2004, November). Discovering personal gazetteers: an interactive clustering approach. In Proceedings of the 12th annual ACM international workshop on Geographic information systems (pp. 266-273). ACM.
\bibitem{YouTube:pasca}
    Toderici, G., Aradhye, H., Pasca, M., Sbaiz, L., \& Yagnik, J. (2010, June). Finding meaning on YouTube: Tag recommendation and category discovery. In Computer Vision and Pattern Recognition (CVPR), 2010 IEEE Conference on (pp. 3447-3454). IEEE.
\bibitem{Foldit:web}
    The Science Behind Foldit. (n.d.). University of Washington, Departments of Computer Science \& Engineering and Biochemistry. Retrieved from \url{https://fold.it/portal/info/about} on June 29, 2018. 
\bibitem{Foldit:results}
    Boyle, A. (2011, September). Gamers solve molecular puzzle that baffled scientists. Cosmic Log.\\
    Retrieved from \url{https://cosmiclog.nbcnews.com/_news/2011/09/18/7802623-gamers-solve-molecular-puzzle-that-baffled-scientists} on June 29, 2018.
\bibitem{Manu:wuest}
    Wuest, T., Weimer, D., Irgens, C., \& Thoben, K. D. (2016). Machine learning in manufacturing: advantages, challenges, and applications. Production \& Manufacturing Research, 4(1), 23-45.
\end{thebibliography}
